INTELLIGENT SYSTEMS

### 2021-03-31 paper_3.tex
continuing 3.4.3

>>>>

\subsubsection{Experimental Results}
Various quality factors (\emph{QS}), useful for indicating the degree of loss in a 
compressed image, are manually set in order to achieve the same bits per 
pixel (\emph{bpp}) of the original image. In order to compare the other methods 
existing at the state of the art with the proposed method, two compression 
quality indices were used such as \emph{PSNR} and \emph{SSIM}. With a \emph{QF} set to 5, the ù
comparison results obtained are shown in figure \ref{fig:QF5}, while the results 
obtained whit \emph{QF} set to 10 are shown in figure \ref{fig:QF10}
\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison.png}
    \centering
    \caption{JPEG: QF=5, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
    \label{fig:QF5}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width = 1 \linewidth]{images/paper3/comparison2.png}
    \centering
    \caption{JPEG: QF=10, PSNR(db) and SSIM results of alghoritms image deblocking and denoising.}
    \label{fig:QF10}
\end{figure}
